Reproducible Research: A Tutorial on how to do the same thing more than once in R

### 2021-08-04 manuscript.Rmd
add summary as code

>>>>

1. Install the `repro` package:

```{r, eval=FALSE}
options(
  repos = c(aaronpeikert = 'https://aaronpeikert.r-universe.dev',
            CRAN = 'https://cloud.r-project.org')
)
install.packages('repro')
```

2. Check the required software:

```{r}
repro::check_git()
repro::check_make()
repro::check_docker()
```

3. Create an R project or use an existing one. Do not forget to add `repro` metadata (i.e. packages, scripts, data).

```yaml
repro:
  scripts:
    - R/load.R
  data:
    - data/mtcars.csv
  packages:
    - tidyverse
```

The example `repro` project already has this metadata:

```{r,eval=FALSE}
repro::use_repro_template("/some/folder")
```

4. Let `repro` generate Docker- and Makfile:

```{r, eval=FALSE}
repro::automate()
```

5. Enjoy automated reproducibility:
